The LBRY Trending Algorithm

### 2021-11-17 tex/ms.tex
Reference

\section{Introduction}
LBRY needs a trending algorithm to rank claims by `recent popularity',
preferably using on-chain information such as changes in support. An
intuitive idea is to have increases and decreases in overall support cause
a `spike' in the trending score, which then fades away over time
(assuming no further changes occur). This idea has formed the basis of all the
implementations that I have written.

@@

>>>>

\section{Introduction}
LBRY \citep{li2020lbry} needs a trending algorithm to rank claims by `recent popularity',
preferably using on-chain information such as changes in support. An
intuitive idea is to have increases and decreases in overall support cause
a `spike' in the trending score, which then fades away over time
(assuming no further changes occur). This idea has formed the basis of all the
implementations that I have written.

@@

\bibliographystyle{plainnat}
\bibliography{references.bib/references}
